Environmental Factors Affecting Water Quality at Toronto Beaches

### 2024-09-24 starter_folder-main/paper/paper.qmd
update

---
title: "Water Quality and Safety at Toronto Beaches"
subtitle: "A Data-Driven Investigation into Seasonal Trends and Public Health Implications"
author: 
  - Ziyuan Shen
thanks: "Code and data are available at: https://github.com/Serena-SHEN1011/Toronto-Beach-Data"
date: 22 September 2024
date-format: long
abstract: "This study examines the water quality and environmental conditions of Toronto beaches based on daily observations collected from May to September each year from 2010 to 2023. The analyses focused on identifying key environmental factors that contribute to water safety warnings, such as temperature, waterFowl presence, and wave action. The results of the study indicate a strong link between rainfall, water temperature fluctuations and the issuance of beach advisories. This study provides valuable insights for policy makers and public health officials to enhance safety measures and management of Toronto's beaches during the peak summer months."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

In summary, we measured real-world temperature, wind, rainfall, turbidity, and waterfowl activity using a variety of instruments and estimation techniques, resulting in quantifiable data entries in the dataset. These measurements form the basis for analysing environmental conditions at Toronto Beach, and transform natural phenomena into structured data that can be analysed to reveal trends, patterns and relationships between different variables.

>>>>

---
title: "Environmental Factors Affecting Water Quality at Toronto Beaches"
subtitle: "Investigation into Seasonal Trends"
author: 
  - Ziyuan Shen
thanks: "Code and data are available at: https://github.com/Serena-SHEN1011/Toronto-Beach-Data"
date: 22 September 2024
date-format: long
abstract: "This study examines the water quality and environmental conditions of Toronto beaches based on daily observations collected from May to September each year from 2010 to 2023. The analyses focused on identifying key environmental factors that contribute to water safety warnings, such as temperature, waterFowl presence, and wave action. The results of the study indicate a strong link between rainfall, water temperature fluctuations and the issuance of beach advisories. This study provides valuable insights for policy makers and public health officials to enhance safety measures and management of Toronto's beaches during the peak summer months."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

In summary, we measured real-world temperature, speed of wind, rainfall, turbidity, and waterfowl activity using a variety of instruments and estimation techniques, resulting in quantifiable data entries in the dataset. These measurements form the basis for analysing environmental conditions at Toronto Beach, and transform natural phenomena into structured data that can be analysed to reveal trends, patterns and relationships between different variables.
